Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-01-04 scagnostics.Rmd
Moved randu example to appendix.

<!--The implementation of scagnostics will always perform a binning step first, before evaluating the measures. The binning will introduce random fluctuations on interpolated tour paths, but we may also consider using it to reduce fluctuations from the discreteness inherent to the index definitions, see in particular the definition of the stringy index. This needs some care however as different values may be preferred for different structures and depending on which index is being considered. Moreover, choosing a binning that is too rough may result in loss of discrimination power as structures can no longer be resolved. As an example we compare in Figure \ref{fig:sprialScagBinning} the scagnostics index traces for the Spiral 1000 dataset when moving from $x_1$-$x_2$ to $x_5$-$x_6$, for three values of the bins parameter entering the hexagonal binning procedure. We find indeed that different values may be preferred depending on the index considered, with the default bins=50 being the better choice for the convex and skinny index, while bins=20 may work better for the stringy index. Note that neither choice results in smooth curves for any of the indexes considered here.-->

@@

<!--### Illustrative example-->

To examine the sensitivity of binning in the MIC PPI, the classic RANDU data [@Marsaglia68], available in R, is used. Binning is defined by $\delta$, where $B(n) = n^{\delta}$. Figure \ref{fig:randuEx} shows the best projection, index value and computing time obtained when optimizing the MIC index with values $\delta = 0.6, 0.7, 0.8$. With small $\delta$, less bins, the structure isn't visible, and with larger $\delta$ the structure is confounded with noise. It does appear that this parameter affects the performace of the MIC index.

<!--Despite the low dimensionality, the small squint angle of the structure means that the identification of the maximum depends strongly on the starting conditions. Empirically we have found that using $\alpha = 0.7$ is most efficient in identifying the structure, while the default value $\alpha = 0.6$ is most likely to miss the structure given equal starting conditions.

\textcolor{red}{Possible interpretation: 0.6 not allowing enough bins to accurately capture the structure, 0.7 good compromise, 0.8 becomes overly sensitive to noise}-->

@@

<!--
### Rotation invariance
Do we want to say anything here? big issue for splines2D measure, but also scagnostics
-->

@@

>>>>

@@

The sensitivity to the binning for calculating the MIC index is examined for one example in the Appendix XXX (add cross reference)

@@

@@

## Binning sensitivity of MIC index
To examine the sensitivity of binning in the MIC PPI, the classic RANDU data [@Marsaglia68], available in R, is used. Binning is defined by $\delta$, where $B(n) = n^{\delta}$. Figure \ref{fig:randuEx} shows the best projection, index value and computing time obtained when optimizing the MIC index with values $\delta = 0.6, 0.7, 0.8$. With small $\delta$, less bins, the structure isn't visible, and with larger $\delta$ the structure is confounded with noise. It does appear that this parameter affects the performace of the MIC index.
